\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?

### 2017-12-16 Data_csv/Paper/paper.tex
fiiinaaaal ??

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

%	One of the crucial objectives after an environmental pollution is to recolonise the area. The first to do that are usually microorganisms, therefore helping them and understand this procedure is one of the important challenges of our time. Using bioaugmentation to help a community regrow is a recent method that can be used to fight against pollution. The two microorganism we chose for our experiment are \textit{Pseudomonas putida} and \textit{Pseudomonas veronii}, as they are able to degrade a widely used hydrocarbonate, toluene. We wanted to know if the addition of one of these strain to a bacterial community extracted from sand would have an effect on the growth of this community. In this experiment we worked with toluene and a sand community extracted from St-Sulpice. Our results are encouraging and would deserve some further experimentations. In the experiment conditions, the final amount of \textit{Pseudomonas} cells was way higher than the Sand Community cells, which means that the overall community was quite different from the starting Sand Community.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}
%alternative beginning

@@

\section{MATERIAL AND METHOD}

@@

\section{RESULTS}
\subsection{Week 1 $\textendash$ SC, PP, PPSC}
\subsubsection{Total cell count comparison}

@@

\section{DISCUSSION}
%While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
%The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (Fig. \ref{barplot}). We see that the proportion of SC is low compared to the overall population ($\cong 5\%$). This would be a problem in a bioremediation context because the original community was almost completely replaced.

%\begin{figure}
%	\centering
%	 
%	\includegraphics[width=8cm]{problem_barplot.PNG}
%	\caption{Proportion of red and green fluorescence in the PV + SC and PP + SC cultures in toluene.}
%	\label{barplot}
%	  
%\end{figure}
%To solve this problem, we would like to analyse this further by trying different culture conditions. Firstly, we would try to have a mixed carbon with toluene substrate. Secondly, it would be great to vary toluene and carbon concentration. Third and final, we would like our conditions to be as close to reality as possible. For example growing the cells in sand would certainly affect their growth and fitness.

Firstly, in other bioaugmentation experiments, one of the main challenges is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.

As PV showed a significantly lower growth on average in toluene in presence of SC than PP, it would be tempting to say that PP would be an even better candidate. However, as said in results section B2, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently. It would be good to test the PP and PV on the same SC.

We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref{problemw1} and \ref{problemw2}.

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences.}
		\label{problemw1}
\end{figure}

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw2.PNG}
		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences.}
		\label{problemw2}

@@

 Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig. \ref{scatter1} and \ref{scatter2}). Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig. \ref{problemw1}) or PVSC (Fig. \ref{problemw2}).

It is even more visible in Fig.\ref{problemflow}. Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene. These graphs are almost identical, and both show a green-only fluorescence.

Our hypothesis is that some PP/PV cells died, but weren’t lysed. Their DNA being still nicely protected they could be stained by SYTO-9. However, their metabolic activities stopped, reducing mCherry fluorescence. Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.
\begin{figure}
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=4.3cm]{PP3T5.png}
		\caption{}
		\label{problemflow1}
	\end{subfigure}%
	\begin{subfigure}{.22\textwidth}
		\centering		
		\includegraphics[width=4.3cm]{PPSC1T5.png}
		\caption{}
		\label{problemflow2}				
	\end{subfigure}
\caption{Scatterplot of a stained PP sample(Fig. \ref{problemflow1}) besides a stained PPSC sample (Fig. \ref{problemflow2}). They look very similar. A lot of PP seem to have lost mCherry (red) fluorescence and have shifted downwards (Fig. \ref{problemflow1}) and look like the supposed SC cells in Fig. \ref{problemflow2}.  }
\label{problemflow}
\end{figure}

\subsection{Improvements}

To circumvent this problem, another tagging method unaffected by cell death could be used. For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered. A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells. This would allow a better differentiation of our communities.
\begin{figure}[H]
	\centering

@@

\end{figure}
Another point that could be interesting to change is the initial concentration of PP and PV. Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV. Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media.

In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
The high quantity of a single strain may have made it easier for them  to outgrow SC over time.

%Finally, as often in the lab, our results seem to unveil more questions than answers. We would have liked, if time allowed it, to perform additional experiments proposed above. Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before. 
%
%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above. The issue with this staining technique might carry some artefacts that should be considered in data interpretation.

In conclusion, in the present state, our study shows interesting results. However, the issue with this staining technique might carry some artefacts that should be considered in data interpretation. If time had allowed it, we would have liked to perform the additional experiments proposed above to solve this issue.

@@

\printbibliography
\vspace*{\fill}
\textit{APPENDIX A on next page}
\clearpage
APPENDIX A

@@

	\begin{figure}
		APPENDIX B

>>>>

\begin{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%alternative beginning

@@

\section{Material and method}

@@

\section{Results}
\subsection{Week 1 $\textendash$ SC, PP, PPSC}
\subsubsection{Total cell count comparison}

@@

\section{Discussion}
%While these results are promising, further analysis and plotting were carried out to ensure reliability of our results. 
%The first drawback of the design we noticed is the proportion of SC cells compared to PP or PV  (Fig. \ref{barplot}). We see that the proportion of SC is low compared to the overall population ($\cong 5\%$). This would be a problem in a bioremediation context because the original community was almost completely replaced.

%\begin{figure}
%	\centering
%	 
%	\includegraphics[width=8cm]{problem_barplot.PNG}
%	\caption{Proportion of red and green fluorescence in the PV + SC and PP + SC cultures in toluene.}
%	\label{barplot}
%	  
%\end{figure}
%To solve this problem, we would like to analyse this further by trying different culture conditions. Firstly, we would try to have a mixed carbon with toluene substrate. Secondly, it would be great to vary toluene and carbon concentration. Third and final, we would like our conditions to be as close to reality as possible. For example growing the cells in sand would certainly affect their growth and fitness.
%

%We noticed a slight drawback when we plotted the count of SYTO-9 stained cells over time, for PP alone and PPSC in toluene in Fig. \ref{problemw1} and \ref{problemw2}.

\subsection{mCherry issue}
The results are promising, however, there is a slight drawback.
Some cells were detected in the SYTO-9 only gate in PP alone and PV alone cultures in both media (Fig. \ref{problemflow}). Fig. \ref{problemflow1} is a representation of PP alone in toluene, and Fig. \ref{problemflow2} of PPSC in toluene, both at the same timepoint. These graphs are almost identical, and more importantly, both show an important count in the SYTO-9 only gate (Fig. \ref{problemw1}, Fig. \ref{problemw2}). We also observe this phenomenon with PV alone.
This is quite surprising, knowing that both PP and PV were tagged with mCherry. This protein emits a
red fluorescence and should cause an upwards shift in the fluorescence graph (as explained in Fig. \ref{scatter1} and \ref{scatter2}) and bring these cells in the mChe + SYTO-9 gate.

Our hypothesis is that some PP/PV cells died, but weren’t lysed. Their DNA is still nicely protected  in the cell and can be stained by SYTO-9. However, their metabolic activities stopped, reducing mCherry fluorescence. Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate. It renders differentiation between PP (or PV) and SC seemingly impossible because they both appear in the same gate. A multivariate analysis using PCA (Principal Component Analysis) and K-means clustering was performed to try to differentiate the two controls (PP alone, SC alone) with other factors (forward-scatter and side-scatter for example), but to no avail.

This issue makes us question whether the significant increase in AUC in the SYTO-9 only in PPSC compared to SC alone is due to an increase of the number of SC or to the presence of theses PP cells presenting low red fluorescence values.

To circumvent this problem, another tagging method unaffected by cell death could be used (Fig. \ref{antibody}). For example, a highly specific antibody to \textit{Pseudomonas putida} could be engineered. A secondary antibody, this time linked to a fluorescent protein would bind the first one and therefore mark all \textit{Pseudomonas putida} cells. This would allow a better differentiation of our communities.

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences. Each point is a replicate, and each line is the mean of the corresponding replicates.}
		\label{problemw1}
\end{figure}

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw2.PNG}
		\caption{Total count of green stained cells in toluene for PV alone and PV with SC during week 2. It showed no significant differences. Each point is a replicate, and each line is the mean of the corresponding replicates.}
		\label{problemw2}

@@

\begin{figure}
	\hspace{-0.3cm}
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=4.3cm]{PP3T5.png}
		\caption{}
		\label{problemflow1}
	\end{subfigure}%
	\begin{subfigure}{.22\textwidth}
		\centering		
		\includegraphics[width=4.3cm]{PPSC1T5.png}
		\caption{}
		\label{problemflow2}				
	\end{subfigure}
	\caption{Scatterplot of a stained PP sample(Fig. \ref{problemflow1}) besides a stained PPSC sample (Fig. \ref{problemflow2}). They look very similar. A lot of PP seem to have lost mCherry (red) fluorescence and have shifted downwards (Fig. \ref{problemflow1}) and look like the supposed SC cells in Fig. \ref{problemflow2}.  }
	\label{problemflow}
\end{figure}

% Indeed, the fact that we get a green-only fluorescence in PP and PV alone is surprising, knowing that both PP and PV were tagged with mCherry, which emits a red fluorescence and causes an upwards shift in the fluorescence graph (as explained in Fig. \ref{scatter1} and \ref{scatter2}). Moreover, the number of green-fluorescent cells in PP or PV alone looks a lot like the number in PPSC (Fig. \ref{problemw1}) or PVSC (Fig. \ref{problemw2}).
% 
%It is even more visible in Fig.\ref{problemflow}. Fig.\ref{problemflow1} is a representation of PP alone in toluene, and Fig.\ref{problemflow2} of PPSC in toluene. These graphs are almost identical, and both show a green-only fluorescence.
% 
%
%Our hypothesis is that some PP/PV cells died, but weren’t lysed. Their DNA being still nicely protected they could be stained by SYTO-9. However, their metabolic activities stopped, reducing mCherry fluorescence. Without the red tag, these cells would shift downwards and remain in the SYTO-9 only gate and can't be differentiated from the SC cells.

%\subsection{Improvements}

%Another point that could be interesting to change is the initial concentration of PP and PV. Indeed we used $10^{6}$ cells of SC and $10^{6}$ cells of PP or PV. Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media. 
%
%In addition, we inoculated the media with the same number of PP or PV with SC and haven't considered the fact that SC community is composed of different bacterial species.
%The high quantity of a single strain may have made it easier for them  to outgrow SC over time.

%Finally, as often in the lab, our results seem to unveil more questions than answers. We would have liked, if time allowed it, to perform additional experiments proposed above. Because in the present state, we got interesting results, but due to some unforeseeable events, we cannot be certain that they are not artefacts due to the issue differentiating the cells we mentioned before. 
%
%Finally, the results of our study open new questions for which we need to perform additional experiments, such as those described above. The issue with this staining technique might carry some artefacts that should be considered in data interpretation.
\begin{figure}[H]
	\centering

@@

\end{figure}
\subsection{Bacterial interactions}
To summarise, growing PP or PV with SC shows no effect on the total cell count compared to growing PP / PV alone. 
\begin{figure}[H]
	\centering

\end{figure}
If we assume this tagging issue is negligible, we can infer on the growth of each population separately within each treatment. In the first week, the data indicates that the presence of PP affects SC differently depending on the media (Interaction: F = 26.62, df = 1, $p = 8,64 \cdot 10^{-4}$).  In toluene, it allows a better growth but has no effect in the mix carbon media.  There is an important effect of the media in absence of PP: SC alone grows significantly less in toluene than in mixed carbon. Furthermore, PP shows an important difference in AUC between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$) and no difference due to the presence of SC.

During the second week, SC behaved differently: it was able to grow in the toluene media, even alone. No significant effect of the media nor of the addition of PV were highlighted by the Anova. 
Similarly to PP, PV had a better growth in toluene than in mixed carbon (F = 784.71, df = 1,
$p = 2.85 \cdot 10^{-9}$). This time however, there was a significant reduction of the number of PV in presence of SC in toluene (F =5.56, df = 1, $p = 0,046$). While not being as significant as our other results, it seems to indicate some competition between them in this type of culture.

It might also be important to notice that even if the AUC of the SYTO-9 gate in PPSC is significantly higher than in SC alone, the proportion of SC in PPSC is very low (about 5%).

To study more deeply these interaction, it might be interesting to change is the initial concentration of PP and PV. Indeed we used 10\textsuperscript{6} cells of SC and 10\textsuperscript{6} cells of PP or PV. Maybe by reducing the initial concentration of PP/PV, we could reduce their competition with SC over resources, and therefore observe a better growth for SC in toluene media.

In addition, we inoculated the media with the same number of PP or PV with SC and haven’t considered the fact that SC community is composed of different bacterial species. The high quantity of a single strain may have made it easier for them to outgrow SC over time.

\subsection{Back to context}
In many bioaugmentation experiments, one of the main challenges is the survival of the inoculated strain in presence of a bacterial community \cite{bouchez} \cite{oldarticle}, particularly in absence of pollutant \cite{nodrawback}.

As PV showed a significantly lower growth on average in toluene in presence of SC than PP, it would be tempting to say that PP would be an even better candidate. However, as said in \textit{Results} section \textit{B2}, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently. It would be good to test the PP and PV on the same SC.

\subsection{Conclusion}

In the present state, our study shows interesting results. However, the issue with this staining technique might carry some artefacts that should be considered in data interpretation. If time had allowed it, we would have liked to perform the additional experiments proposed above to solve this issue.

@@

\printbibliography
\vspace*{\fill}
\textit{APPENDIX A on next page}
\clearpage
\section*{Appendix A}

@@

	\begin{figure}
		\section*{Appendix B}
